### 2021-11-16 thesis/tex/nsiTheory.tex
update

\subsection{Altering the Matter Potential}
Up until now, we have only considered weak neutrino interactions with electrons, protons, and neutrons.
We can phenomenologically allow these interactions to include the up and down quarks which are present 
in the Earth as the fundamental components of neutrons and protons, as seen in the Lagrangians
\begin{align*}
    \mathcal{L}_{\mathrm{CC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f f^{\prime} X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \ell_{\beta}\right)\left(\bar{f}^{\prime} \gamma_{\mu} P_{X} f\right) \\
    \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align*}
where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$. The CC NSI effect affects neutrino production and detection, and will not be considered further. NC NSI affect the matter potential, 
and is thus of interest to us.

>>>>

\subsection{Non-Standard Effects on Neutrino Matter Interactions}
Up until now, we have only considered weak neutrino interactions with electrons, protons, and neutrons.
We can phenomenologically allow these interactions to include the up and down quarks which are present 
in the Earth as the fundamental components of neutrons and protons, as seen in the Lagrangians
\begin{align*}
    \mathcal{L}_{\mathrm{CC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f f^{\prime} X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \ell_{\beta}\right)\left(\bar{f}^{\prime} \gamma_{\mu} P_{X} f\right) \\
    \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align*}
where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$. The CC NSI effect affects neutrino production and detection, and will not be considered further. NC NSI affect the matter potential, 
and is thus of interest to us.
